
%----------------------------------------------------------------------------------------
%	IT/COMPUTING SKILLS SECTION
%----------------------------------------------------------------------------------------

\section{Experience}

\skillgroup{Google Summer of Code}
{
	{Wine, implemented by C, is a compatibility layer capable of running Windows applications on several %\\
	POSIX-compliant operating systems, such as Linux and macOS. Wine translates Windows API %\\
	calls into POSIX calls, allowing you to integrate Windows applications into Linux and %\\
	macOS desktop.\\ \\}
	{2014: Implemented IHTMLTable and related Component Object Model (COM) interfaces in wine's mshtml.dll, allowing Wine to handle DOM Objects like \textit{table} to render forms in web pages.}\\
	{2015: Implemented COM interfaces including IHTMLXMLHttpRequest, which is necessary \\
	for transferring data between client and server. Located and fixed a few related memory bugs in msxml.dll.}
}


\skillgroup{Mozilla Committer}{
 2014 - now: Commit Access (Level 1) \\
 
 Switching to new version GCC(6+) 
 caused massive compile warnings for Gecko (Firefox engine). 
 I involved in code quality control process for reporting and fixing these C++ defects.
}


\skillgroup{Author of package \textit{momap} for Python3}{
	<multimap> is a container in C++ STL. I ported it to Python3, so I can use \textit{momap}
	in my Python script handling research data in my lab. 
}

\skillgroup{Contributor and Maintainer of Shanghai Jiaotong University's Open Source Mirror}
{
2016 - 2017: Shanghai Jiaotong University's Linux Group set up a new open source mirror.
I encapsulated the program for mirror into Docker images, which provides extensibility
and flexibility for our program. After alpha test, I migrated the program into another server.
}

\vspace{-5mm}

\section{Skills}
\skillgroup{Programming Language}
{ C, C++, Python
	}
\skillgroup{Tools}
{Git, Docker, dnf, vim, make
	}
%\section{ Honors \& Awards }
%\interestsgroup{
%	\interest{2014 Excellent Scholarship, School of Pharmacy}
%	\interest{2015 Rank A Scholarship, School of Pharmacy}
%	\interest{2016 Rank B Scholarship, School of Pharmacy}
%	\interest{2015 DataBang 2nd place}
%}
%




